### 2021-09-08 manuscript/methodology.tex
bring files from presubmission branch

PAREI AQUI

Figure \ref{fig:flops} shows a comparative between the methods varying the number of observation points up to $1,000,000$, where it is possible to observe a reduction of $10^7$ orders of magnitude to estimate parameter vector $\mathbf{\hat{p}}$ in relation to the non-iterative classical method and $10^3$ orders of magnitude in relation to the standart CGLS algorithm using $50$ iterations. 
%A more detailed, step by step, flops count of the classical and CGLS algorithm can be found in Appendix A.

In Figure \ref{fig:solve_time} we show the time necessary to construct matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}) and solve the linear system up to $10,000$ points of observation. With this dataset the classical method takes more than sixty-three seconds, the CGLS more than twelve seconds, while our method takes only half a second. The cpu used for this test was a intel core i7-7700HQ@2.8GHz.

@@

In Table \ref{tab:RAM-usage} there is comparison between how much RAM memory is adressed to store the sensitivity matrix for each of the methods. The classical approach and the CGLS have to store the whole matrix $\mathbf{A}$ (equation \ref{eq:aij_mag}), this means that a dataset  with for example $N = 10,000$ observation points, the sensitivity matrix has $N^2 = 100,000,000$ elements and takes approximately $763$ Megabytes of memory (8 bytes per element). For our method, it is necessary to store the first six columns of each of the components from matrix $\mathbf{H}$ (equation \ref{eq:Hi}) embedded into the BCCB matrices. With the same dataset $N = 10,000$ it needs $1.831$ Megabytes. After completing the steps to store the eigenvalues of matrix $\mathbf{C}$ (equation \ref{eq:w_Cv}) it takes only $0.6104$ Megabytes. Here, we are considering 16 bytes per element as the eigenvalues are complex numbers resulting from the 2D FFT. For a bigger dataset as $N = 1,000,000$ the amount of RAM necessary goes to $7,629,395$, $183.096$ and $61.035$ Megabytes, respectively, showing the necessity to find improved and efficient methods for the equivalent layer technique as the one presented in this work. We remember that throughout our work we are always considering $N = M$.

% <========== in review

>>>>

Figure \ref{fig:flops} shows a comparison between 
$f_{classical}$ (equation \ref{eq:flops-classical-method}), 
$f_{cgls}$ (equation \ref{eq:flops-standard-cgls}) and 
$f_{conv}$ (equation \ref{eq:flops-convolutional-method})
for different numbers of observation points up to $1,000,000$. As we can see, 
the total flops count associated with our method is $10^7$ orders of magnitude smaller 
than that associated with the classical method and $10^3$ orders of magnitude smaller than
that associated with the standard CGLS method by using a maximum number
of iterations $N^{it} = 50$.

Figure \ref{fig:solve_time} shows the time necessary to build matrix $\mathbf{A}$ 
(equation \ref{eq:A_expand}) and solve the linear system for $N$ varying up to $10,000$. 
With $N = 10,000$, the classical method takes more than sixty-three seconds, the standard 
CGLS more than twelve seconds, while our method takes only half a second. 
The CPU used for this test was a Intel Core i7-7700HQ@2.8GHz.

@@

Table \ref{tab:RAM-usage} shows a comparison between the RAM memory storage 
associated with each method. The classical and standard CGLS methods have to store the whole 
matrix $\mathbf{A}$ (equation \ref{eq:A_expand}). For example, a dataset with 
$N = 10,000$ observation points has an associated sensitivity matrix $\mathbf{A}$ formed by 
$N^2 = 100,000,000$ elements and takes approximately $763$ Megabytes of memory (8 bytes per element). 
Using the same number of observation points $N = 10,000$, our method requires only 
$1.831$ Megabytes to store the first columns of the BCCB matrices
$\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) and 
$0.6104$ Megabytes to store the complex matrix $\mathbf{L}$ (equation \ref{eq:L}) 
(16 bytes per element). For a bigger dataset with $N = 1,000,000$, the amount of necessary RAM 
goes to $7,629,395$, $183.096$ and $61.035$ Megabytes, respectively.
